---
title: "uwstaffshw"
author: "Frederick Kim"
date: "2/5/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# setups 1
rm(list=ls())

# Data Importation
address <- "https://guide.wisc.edu/faculty/"
mytext <- readLines(address)
```

check the structure of the raw data
```{r}
str(mytext)
head(mytext)
```

Let's cheat here. Find the index of the list that contains the name "AARLI,LISA" and see the structure.
```{r}
name <- "AARLI,LISA"
grep(name, mytext)
```

It's the 164th element! let's look at that one
```{r}
mytext[163] 
```

from what I understand, the staff memebers' information are stored 
alphabetically and 164th element is information of staffs whose surname starts 
with A 165th = B, 166th = C, ...

I assume every personal data starts with <ul class=\"uw-people\">
My hypothetical structure of personal data in the html data: (general)>
<ul class=\"uw-people\">  <li> <p> Name of the instructor <br/>  position  <br/> program and year <br/></p></li><li><p> name of the instructor ...

```{r}           
staff_line <- strsplit(x = mytext, split = c('<ul class=\"uw-people\">'))

uw_staffs <- list("name" = list(), "position" = list(), "department" = list(), "degree information" = list())



for(idx in (163:188)){
  dummy <- unlist(staff_line[[idx]])
  
  dummy2 <- strsplit(x = dummy, split = '<li><p>')

  dummy3 <- strsplit(x = dummy2[[2]], split = '<br/>')
  
  for(info in dummy3){
    uw_staffs$name <- c(uw_staffs$name, info[1])
    uw_staffs$position <- c(uw_staffs$position, info[2])
    uw_staffs$department <- c(uw_staffs$department, info[3])
    uw_staffs$`degree information` <- c(uw_staffs$`degree information`, info[4])
  }
  
}

```